{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-09-08 wacv_for_review.tex
Hyperrefs added, spellcheck done

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and exten0))ds amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

@@

The KCF solves essentially the problem of a regression in the form of
the regularization:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equation \ref{eq:Closedform_RidgeReg} exists. To make the
closed-form solution less complex, an element-wise, multiplication in
frequency domain was proposed for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of this closed-form solution is proposed to make
it more robust to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $w$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
one can execute an object detection using this kernelized correlation
filter with multi-channel features as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area, translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area is tended to be noisy and less discriminative and adding color
information makes the feature vector for the translation filter,
$R_{t}^{L}$, more robust to noise and more discriminative. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. But,
this is not the case for the small area, translation filter,
$R_{t}^{S}$, because this translation filter does not contain much of
the background area around the target. Figure \ref{fig:Filters}(a)
shows an example of this translation filter. Lastly, we use both fHoG
and color-naming features again for the scale filter,
$R_{s}$. Although we are using the same feature representations for
the scale filter learning relatively smaller area just around the
target, the reason of using two feature sets is slightly different in
that the area to learn is too small for the fHoG to represent the area
well. In addition, the scale filter, explained earlier in the
algorithm \ref{alg:MKCF}, estimates the scale of a target by
correlating it with three candidate ROIs. This search may increase the
run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
practical, we use a smaller template size (i.e., 64$\times n$) for the
scale filter, $R_{s}$. The smaller template size does not degrade the
tracking performance neither because of 1) zero padding around the
target and 2) use of color feature.
\begin{comment}
The ROI considered by $R_{s}$ is resized to a smaller template
resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
This leads to less discriminative shape features. To reduce the noise
in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
scale by correlating the filter with three candidate ROIs as detailed
in alg.~\ref{alg:MKCF}.  This increases the complexity from
$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
reduce the number of operations, we assign a smaller template size to
$R_{s}$.  This does not degrade the tracking performance due to two
reasons: (1) zero padding around the target and (2) integration of
color features. This way, we keep the run-time complexity of the
$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of
$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
systems.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board, embedded
system. To this end, we used two conventional features, fHoG and
color-naming for the {\it E}nKCF. At the same time, we observed that
the feature vectors learned from DNN have been used to improve the
performance of the trackers based on KCF \cite{ma2015hierarchical,
  danelljan2015convolutional}, and some of the single-board, embedded
systems have GPUs. We believe that the performance of the {\it E}nKCF
could be also improved with deep convolutional features trained on ImageNet dataset.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and exten0))ds amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}
\usepackage[hidelinks]{hyperref}

@@

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equation \ref{eq:Closedform_RidgeReg} exists. To make the
closed-form solution less complex, an element-wise multiplication in
frequency domain was proposed for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of this closed-form solution is proposed to make
it more robust to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $w$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
one can execute an object detection using this kernelized correlation
filter with multi-channel features as
\begin{equation}
r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
\end{equation}
where $r$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

We use both fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} for the large area, translation filter,
$R_{t}^{L}$. This is because the fHoG applied to relatively larger
area is tended to be noisy and less discriminative and adding color
information makes the feature vector for the translation filter,
$R_{t}^{L}$, more robust to noise and more discriminative. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. But,
this is not the case for the small area, translation filter,
$R_{t}^{S}$, because this translation filter does not contain much of
the background area around the target. Figure \ref{fig:Filters}(a)
shows an example of this translation filter. Lastly, we use both fHoG
and color-naming features again for the scale filter,
$R_{s}$. Although we are using the same feature representations for
the scale filter learning relatively smaller area just around the
target, the reason of using two feature sets is slightly different in
that the area to learn is too small for the fHoG to represent the area
well. In addition, the scale filter, explained earlier in the
algorithm \ref{alg:MKCF}, estimates the scale of a target by
correlating it with three candidate ROIs. This search may increase the
run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
practical, we use a smaller template size (i.e., 64$\times n$) for the
scale filter, $R_{s}$. The smaller template size does not degrade the
tracking performance neither because of 1) zero padding around the
target and 2) use of color feature.
\begin{comment}
The ROI considered by $R_{s}$ is resized to a smaller template
resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
This leads to less discriminative shape features. To reduce the noise
in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
scale by correlating the filter with three candidate ROIs as detailed
in algorithm~\ref{alg:MKCF}.  This increases the complexity from
$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
reduce the number of operations, we assign a smaller template size to
$R_{s}$.  This does not degrade the tracking performance due to two
reasons: (1) zero padding around the target and (2) integration of
color features. This way, we keep the run-time complexity of the
$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of
$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
systems.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at $30$fps on a single-board, embedded
system. To this end, we used two conventional features, fHoG and
color-naming for the {\it E}nKCF. At the same time, we observed that
the feature vectors learned from CNN have been used to improve the
performance of the trackers based on KCF \cite{ma2015hierarchical,
  danelljan2015convolutional}, and some of the single-board, embedded
systems have GPUs. We believe that the performance of the {\it E}nKCF
could be also improved with deep convolutional features trained on ImageNet dataset.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.
